### 2014-03-15 docs/paper.tex
Comments for stuff to write.
Lots more on GoAgent.

% Lantern
% Psiphon

@@

GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
Engine and Host header--based domain fronting. GoAgent requires users to upload
a personal copy of the server code to App Engine, and works only with HTTP and HTTPS,
not other TCP-based protocols.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

>>>>

% Lantern
% Psiphon
% Infranet
% Freegate
% Ultrasurf

@@

GoAgent~\cite{goagent} is a direct inspiration for our system in its use of App
Engine and Host header--based domain fronting.
As in our system, traffic is fronted by the Google frontend server
and delivered to its destination by a specialized app running on App Engine.
GoAgent requires users to upload a personal copy of the server code to App Engine,
which harms usability but requires no central management
and enables users to stay within bandwidth limits that exist for unpaid apps.
GoAgent is an HTTP and HTTPS proxy only.
It works by encapulating a desired HTTP request, including URL and POST body, if any,
and uploading the request to App Engine.
The app unpacks the encapsulated request and directly requests the desired URL using
App Engine's URL-fetching API.
The design is simple but has disadvantages, stemming from the web app's
need to know what URL to request.
In order to proxy HTTPS, the local GoAgent proxy program does a benign man-in-the-middle
attack on the browser, which must have previously trusted the GoAgent CA certificate.
The local proxy program decrypts the HTTPS in order to read from it the HTTP request including the URL.
When the response comes back, the local proxy re-encrypts it under its own key.
End-to-end security is lost; an attacker positioned at the web app
is able to observe and modify all traffic.
In our system, such an attacker may only deny service or perform traffic analysis on ciphertext.
Additionally, we allow proxying of any TCP-based traffic, not only HTTP.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

\section{Future work}

% Pipelining of requests.
% Put a diagram here showing serialized requests.
% Simple reliability layer, SEQ/ACK.
% Would be useful for Iran-like session cutoff, independent of meek.
